The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-04-06 ms.tex
Write a bit about proper motions

    (6)~Total velocity: \(V_{\text{tot}} = ( V_{\text{los}}^2 + V_{\text{pos}}^2 )^{1/2}\).
    (7)~Inclination of velocity vector to line of sight: \(\tan i = V_{\text{los}} / V_{\text{pos}}\).

@@

Combine radial velocities with proper motions.

>>>>

    (6)~Total pattern velocity: \(V_{\text{tot}} = [ (1.2 V_{\text{los}})^2 + V_{\text{pos}}^2 ]^{1/2}\) (see text for explanation of the factor 1.2).
    (7)~Inclination of velocity vector to line of sight: \(\tan i = 1.2 V_{\text{los}} / V_{\text{pos}}\).

@@

For those nebular features where both proper motion and radial velocity measurements exist,
it is possible to estimate the full three-dimensional velocity vector.
Under the assumption that all motions are strictly radial,
one can also find the three-dimensional position.
These are given in Table~\ref{tab:3d} for a wide variety of nebular features
in the inner shells, intermediate shell, low-ionization knots, and outer lobes.

When combining radial velocities and proper motion measurements,
it is necessary to account for the fact that radial velocities measure the material speed,
whereas proper motions measure pattern speeds of shocks or ionization fronts \citep{Mellema:2004a}. 
The exact correction factor (material speed divided by pattern speed)
is model-dependent (e.g., Appendix~A of \citealp{ODell:2009c}),
but is predicted to be generally larger than unity
\citetext{see Fig.~8 of \citealp{Jacob:2013a}}
unless the nebula is in the recombination phase.
For simplicity, we adopt a constant correction factor of 1.2 for all entries in Table~\ref{tab:3d},
which is consistent with the predicted value for expansion velocities greater than \SI{30}{km.s^{-1}}
\citetext{see Fig.~5 of \citealp{Schonberner:2018a}}.

Note that the uncertainties given in the table are derived from observational errors only,
and they do not include the systematic uncertainty in the distance
